Reanalysis Step 6: Sensitivity Analysis with E-values

### 2025-09-01 reanalysis-6-sensitivity-interaction.qmd
fix evalues

# Load results from previous steps
ps_results <- readRDS(file.path(reanalysis_data_dir, "ps_results_twang.rds"))

# Load outcome analysis results (from step 4)
outcome_results <- readRDS(file.path(reanalysis_data_dir, "outcome_analysis_results.rds"))
pooled_results <- outcome_results$pooled_coefficients
subgroup_effects <- outcome_results$subgroup_effects
```

@@

>>>>

# Initialize logging
log_file <- init_log("sensitivity_analysis_interaction")

# Load outcome analysis results from interaction analysis
outcome_results <- readRDS(file.path(reanalysis_data_dir, "outcome_analysis_results.rds"))
pooled_results <- outcome_results$pooled_coefficients
subgroup_effects <- outcome_results$subgroup_effects
```

@@

```{r finalize-log}
#| include: false
# Finalize logging
log_message("Sensitivity analysis with E-values completed successfully")
final_log <- finalize_log(success = TRUE)
```
